Proposed Solution

### 2017-01-25 CAV17/secs/intro.tex
stuff

This paper presents \app, the first automatic verification framework
for general software configurations, by overcoming the above two
obstacles. In general, \app verifies a given configuration file $F$ 
through three steps:

\para{Step~1: Translator}
\app takes as input a large training set of configuration files
belonging the same system as $F$,
and we do not have any assumption on the correctness of these files.
\app analyzes the training set, and generates a well-structured and
probabilistically-typed intermediate representations.

\para{Step~2: Learning}
\app derives configuration rules by running {\em rule association
learning} algorithm to learn the generated intermediate representations.
The insight of our design is: every file in the training set
contains several different errors and these errors only appear 
in a small percentage of files. Based on this insight,
we are able, with the help of the probabilistic cutoff, to learn a
set of configuration rules. These rules, in general, specify 
which properties the entries in configuration files need to satisfy. 
One can see this learning process as a way of deriving  
a specification for configuration files.  
Once a specification is obtained, we can do verification that 
uses these learned rules to check the correctness of 
the configuration files
of interest and detect potential errors.

>>>>

Our learning algorithm surmounts all of difficulties present in 
existing tools.  \app implements a learning
algorithm inspired by {\em rule association
learning}~\cite{agrawal1993mining}. It analyzes a large training set of configuration  files~\cite{configdataset}. Those are real-world reported misconfigurations. A file in the training set might 
contain several different errors and these errors only appear 
in a small percentage of files. We first translate those file into an 
intermediary typed language. With with every type we associate 
a set of very general templates. The user does not
need to provide any templates, they are internally associated to the types.

 algorithm to learn the generated intermediate representations.
The insight of our design is: every file in the training set
contains several different errors and these errors only appear 
in a small percentage of files. Based on this insight,
we are able, with the help of the probabilistic cutoff, to learn a
set of configuration rules. These rules, in general, specify 
which properties the entries in configuration files need to satisfy. 
One can see this learning process as a way of deriving  
a specification for configuration files.  
Once a specification is obtained, we can do verification that 
uses these learned rules to check the correctness of 
the configuration files
of interest and detect potential errors.
